---
title: "introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Introduction

The `LinearRegressionR` package provides a set of tools for fitting, summarizing, and evaluating linear regression models. 
This vignette demonstrates how to use the package, including:
- Fitting a linear regression model
- Predicting new values
- Performing ANOVA
- Visualizing model diagnostics
- Comparing the package's performance with base R functions.

```{r setup}
library(HW3.625.2)
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(sas7bdat)
library(here)
```

# Simulating Data

First simulate data for demonstration.

```{r simulate-data}
data <- read.sas7bdat(here("data", "completedata-1.sas7bdat"))
head(data)
```
# Fitting a Model
Fit a linear regression model using the `linear_regression` function.

```{r fit-model}
Y <- data$Depression
X <- data[, c("Fatalism", "Spirituality")]
fit <- linear_regression(X, Y)
print(fit$coefficients)
```
# Model Summary

Summarize the fitted model using the `summary` function.

```{r summary-model}
summary.linear_regression(fit)
```
# Predicting New Values

Use the `predict` function to predict responses for new data.

```{r predict-values}
newdata <- data.frame(
  Fatalism = c(3.5, 4.2),  
  Spirituality = c(2.1, 3.8)
)
predictions <- predict.linear_regression(fit, newdata)
print(predictions)
```
# Performing ANOVA

Evaluate the model using analysis of variance (ANOVA).

```{r anova-analysis}
anova_results <- anova.linear_regression(fit)
print(anova_results)
```

# Comparison with Base R

Compare the coefficients and performance of `LinearRegressionR` with base R's `lm`.
```{r comparison-baseR}
fit_lm <- lm(Depression ~ Fatalism + Spirituality, data = data)

# Extract coefficients from both models
linear_regression_coefficients <- fit$coefficients
lm_coefficients <- coef(fit_lm)  

# Compare coefficients element-wise
comparison <- data.frame(
  Feature = paste0("X", 1:length(linear_regression_coefficients)),
  LinearRegressionR = linear_regression_coefficients,
  BaseR = lm_coefficients
)
comparison

```

```{r}
# Comparison of Summary in MyPackage Results
output_1 <- summary.linear_regression(fit)
```

```{r}
# Comparison of Summray in BaseR
output_2 <- summary(fit_lm)
print(output_2)
```
```{r}
#compare the prediction output
#Outcome of linear regression method
predictions <- predict.linear_regression(fit, newdata)


#Outcome of prediction baseR
lm_predictions <- predict(fit_lm, newdata)

comparison_prediction <- data.frame(
  Predictions = predictions,
  BaseR = lm_predictions
)
comparison_prediction
```
```{r}
library(microbenchmark)
benchmark_results <- microbenchmark(
  Custom = linear_regression(X, Y),
  BaseR = lm(Depression ~ Fatalism + Spirituality, data = data),
  times = 100
)
print(benchmark_results)
```
